\documentclass[Chap2main.tex]{subfiles}

% Load any packages needed for this document

\begin{document}
	
\section{Variations of the Bland-Altman Plot} Referring to the
assumption that bias and variability are constant across the range
of measurements, \citet{BA99} address the case where there is an
increase in variability as the magnitude increases. They remark
that it is possible to ignore the issue altogether, but the limits
of agreement would wider apart than necessary when just lower
magnitude measurements are considered. Conversely the limits would
be too narrow should only higher magnitude measurements be used.
To address the issue, they propose the logarithmic transformation
of the data. The plot is then formulated as the difference of
paired log values against their mean. Bland and Altman acknowledge
that this is not easy to interpret, and may not be suitable in
all cases.

\citet{BA99} offers two variations of the Bland-Altman plot that
are intended to overcome potential problems that the conventional
plot would inappropriate for. The first variation is a plot of
case-wise differences as percentage of averages, and is
appropriate when there is an increase in variability of the
differences as the magnitude increases. The second variation is a
plot of case-wise ratios as percentage of averages. This will
remove the need for $log$ transformation. This approach is useful
when there is an increase in variability of the differences as the
magnitude of the measurement increases. \citet{Eksborg} proposed
such a ratio plot, independently of Bland and Altman.
\citet{Dewitte} commented on the reception of this article by
saying `Strange to say,this report has been overlooked'.

\section{Variations of the Bland Altman Plot}
\citet{BA99} offers two variations of the Bland -Altman plot that
are intended to overcome potential problems that the conventional
plot would inappropriate for.

The first variation is a plot of casewise differences as
percentage of averages, and is appropriate when there is an
increase in variability of the differences as the magnitude
increases.


% When selecting this option the differences will be expressed as
% percentage of the averages. This option is useful when there is an
% increase in variability of the differences as the magnitude of the
% measurement increases.


The second variation is a plot of casewise ratios as percentage of
averages.

% Plot ratios When this option is selected then the ratios of the
% measurements will be plotted instead of the differences (avoiding
% the need for log transformation). This option as well is useful
% when there is an increase in variability of the differences as the
% magnitude of the measurement increases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage








\subsubsection{Classifying outliers and recalculating} We opted to
examine this matter in more detail. The following points have to
be considered:
\\
\indent How to suitably identify an outlier (in a generalized sense)
\\
\indent Would a recalculation of the limits of agreement generally
results in  a compacted range between the upper and lower limits
of agreement?
\newpage

\end{document}
